---
title: "Descriptive Analysis"
author: "Nilabja Ray"
date: "8 May 2018"
output: html_notebook
---



```{r setup, include=FALSE}
rm(list=ls())
cat('\014')
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('..'))
library(data.table)
library(ggplot2)
library(zoo)
library(stringr)
```

### Variable Summaries
```{r load_data}
dat = readRDS('data/finaldatajan17.RDS')
```

#### 1. Location
It is a factor with `r uniqueN(dat$Location)` levels. The interaction with target variable is as shown below:
```{r location, paged.print=TRUE}
dat[,.(acc_count = .N,target_positive = sum(target),perc=sum(target)*100/.N),Location][order(-acc_count,-perc)]
```
The Number of levels is too high to have clear idea about impact of location on target. 

#### 2. State
Factor with `r uniqueN(dat$State)` levels. 

```{r state}
dat[,.(acc_count = .N,target_positive = sum(target),perc=sum(target)*100/.N),State][order(-acc_count,-perc)]

```
The rate of delinquincy is higher for Delhi, Maharashtra and Karnataka. Punjab also is high, but sample size is too small. 

**Only state will be used in the model - location will not be used.**

We used this variable to create the flag `isAgri`. 
```{r}
dat[,.(acc_count = .N,target_positive = sum(target),perc=sum(target)*100/.N),AgriFlag][order(-acc_count,-perc)]
```

i.e. Non-agri products have higher default rate than agri products.

#### 3. LoanPurpose
Factor with `r uniqueN(dat[,Loan_purpose])` levels. 

```{r}
dat[,.(acc_count = .N,target_positive = sum(target),perc=sum(target)*100/.N),LoanPurpose][order(-acc_count,-perc)]
```

Loan for new body has higher dq rate than other purposes. 

#### 4. BorrowerDesc
Factor with `r uniqueN(dat[,BorrowerDesc])` levels. 

```{r}
dat[,.(acc_count = .N,target_positive = sum(target),perc=sum(target)*100/.N),BorrowerDesc][order(-acc_count,-perc)]
```

TRANSPORTER A CATEGORY has exceptionally high default potential. 

#### 5. BorrowerType


```{r}
dat[,.(acc_count = .N,target_positive = sum(target), perc=sum(target)*100/.N), 
    BorrowerType][order(-acc_count,-perc)]

```

#### 6. DisbAmt

Continuous variable. Can be binned to convert to categorical. 
**Summary**
```{r}
summary(dat$DisbAmt)
```

In order to check the impact of DisbAmt on our target varibale, we conduct a non-parametric comparison of the variable for target=0 and target=1. 

```{r}
wilcox.test(DisbAmt~target,data=dat)
```

Since the P-value is small enough, we conclude that the DISB_AMT has some impact on the target. For better visualisation, a violin plot is created. 

```{r}
ggplot(dat,aes(target,DisbAmt))+geom_violin(scale = "count")
```

#### 7. ROI
Numeric variable 

```{r}
summary(dat$ROI)
```

** Mann-Whitney U Test **
```{r}
wilcox.test(ROI~target,data=dat)
```

Since there is no significant difference in the roi for target 0 and target 1, it will not be included in the model. 

#### 10. ManufacturerDesc
Factor - has `r uniqueN(dat$ManufacturerDesc)` levels. 

```{r}
dat[,.(acc_count = .N,target_positive=sum(target),perc=sum(target)*100/.N),
    ManufacturerDesc][order(-perc)]
```
It is found that the default rate is higher for Private Body Builders. 

#### 11. VehicleCategory
Factor with `r uniqueN(dat[,VehicleCategory])` levels. 

```{r}
dat[,.(acc_count = .N,target_positive=sum(target),perc=sum(target)*100/.N),
    VehicleCategory][order(-perc)]
```

** Joint Distribution of VehicleCategory and ManufacturerDesc

```{r fig.height=8, fig.width=12}
tempdat= dat[,.(acc_count =.N, target_positive=sum(target), perc=sum(target)*100/.N),
             by=.(ManufacturerDesc,VehicleCategory)]
a = ggplot(data=tempdat,aes(x=ManufacturerDesc,y=VehicleCategory))+
  geom_point(aes(size=acc_count,fill=perc),shape=21,alpha=.9)+
  scale_size(range = c(5, 20)) +
  theme(axis.text.x = element_text(angle=60,hjust=1))+
  scale_x_discrete(labels=function(x) str_wrap(x,15))
a+scale_fill_distiller(palette = "RdYlGn")

```


#### 12. AssetCost

Continuous variable

```{r}
summary(dat[,AssetCost])
```

**Loan to Asset Cost Ratio**

Created the new column - continuous
```{r}
dat[,LAR:=DisbAmt/AssetCost]
summary(dat[,LAR])
dat[,mean(LAR),target]
wilcox.test(LAR~target,data=dat)
wilcox.test(DisbAmt~target,data=dat)
wilcox.test(AssetCost~target,data=dat)
```
LAR has significant impact on target. 

#### 13. AssetLevel

```{r}
dat[,.(acc_count = .N,target_positive=sum(target),perc=sum(target)*100/.N),
    AssetLevel][order(-perc)]
```

#### 14. POS

```{r}
summary(dat[target==TRUE,POS])
summary(dat[target==FALSE,POS])
wilcox.test(POS~target,data=dat)

```

#### 15. DPDDays

```{r}
summary(dat[,DPDDays])
summary(dat[target==TRUE,DPDDays])
summary(dat[target==FALSE,DPDDays])
```



```{r}
dat[,.N,DPDDays]
```

#### 16. BounceFlag


```{r}
addmargins(prop.table(xtabs(N~BounceFlag+target,data=dat[,.N,.(target,BounceFlag)]),margin = 1),2)
```

#### 17. ever60Flag, ever30Flag, everXFlag

```{r}
temp_tot = dat[,.(.N,target_positive=sum(target))]
temp_x = dat[everXFlag==TRUE,.(.N,target_positive=sum(target))]
temp_30 = dat[ever30Flag==TRUE,.(.N,target_positive=sum(target))]
temp_60 = dat[ever60Flag==TRUE,.(.N,target_positive=sum(target))]
temp=rbind(temp_tot,temp_x,temp_30,temp_60)

temp[,perc:=100*target_positive/N]
rm(temp_30,temp_60,temp_tot,temp_x)
cbind(filter=c('None','ever_x','ever_30','ever_60'),temp)
```

#### 18. BounceCount

```{r}
summary(dat[,BounceCount])
temp=dat[,.(.N,target_positive=sum(target)),cut(BounceCount,breaks = c(0,1,10,20,30,100),right = FALSE)]
temp[,perc:=target_positive*100/N][order(-perc)]
```

#### 19. AgriFlag

```{r}
addmargins(prop.table(xtabs(~AgriFlag+target,data=dat),1),2)
```

#### 20. BorrowerCategory


```{r}
dat[,.(acc_count = .N,target_positive=sum(target),perc=sum(target)*100/.N),
    BorrowerCategory][order(-perc)]
```

#### 21. CashPayFlag

```{r}
dat[,.(acc_count = .N,target_positive=sum(target),perc=sum(target)*100/.N),
    CashPayFlag][order(-perc)]
```

#### 22. BR6m,BR3m,BRLife

```{r}

summary(dat[CashPayFlag==FALSE,BR6m])
summary(dat[CashPayFlag==FALSE,BR3m])
quantile(dat[,BR6m],c(1:10)/10,na.rm = TRUE)
sum(is.na(dat[CashPayFlag==FALSE,BR6m]))
sum(is.na(dat[CashPayFlag==FALSE,BR3m]))
dat[,.N,BR6m]
```



23. MOB


```{r}
summary(dat$MOB)
summary(dat[target==TRUE,MOB])
summary(dat[target==FALSE,MOB])
```
