---
title: "Commercial Vehicle PD model"
output: html_notebook
author: Nilabja Ray
---
### Variable Description
```{r include=FALSE}
rm(list=ls())
cat('\014')
library(data.table)
getwd()
flist = file.path('data','monthly_report',list.files(file.path('data','monthly_report')))
dat = lapply(flist,fread,colClass='character')
dat = do.call(rbind,dat)
```

#### 1. ApplicationID, AGREEMENT_NO
- **Type:** Numeric/Alphanumeric string
- **Description:** Primary identifier for individual data-points. 
```{r}
print(dat[,uniqueN(ApplicationID),])
print(dat[,uniqueN(AGREEMENT_NO),])

```
#### 2. final_cif_no
- **Type:** Numeric String 
- **Description:** Primary identifier for Customers.  
```{r}
print(dat[,uniqueN(final_cif_no),])
dat[,.(acc_count=uniqueN(ApplicationID)),by=final_cif_no][order(-acc_count)]
```
#### 3. Location
- **Type:** String
- **Description:** City/Town name

```{r}
dat[,.(acc_count=uniqueN(ApplicationID)),by=Location][order(-acc_count)]
```

#### 4. state
- **Type:** String
- **Description:** Name of state where loan was disbursed 
```{r}
dat[,.(acc_count=uniqueN(ApplicationID)),by=state][order(-acc_count)]
```

#### 5. CV_Old_New_flag
- **Type:** Bool
- **Description:** Whether new or resell vehicle. Only New vehicle data to be used.  
```{r}
unique(dat[,CV_Old_New_flag])
dat[CV_Old_New_flag=='',CV_Old_New_flag:='Old']
dat=dat[CV_Old_New_flag=='New']
```
#### 6. Product
- **Type:** Factor
- **Description:** Types of Loan Product. 4 different levels. 
```{r}
dat[,.(account_count=uniqueN(ApplicationID)),by=Product]
```
#### 7. Loan_purpose
- **Type:** Factor
- **Description:** Purpose of the loan. 10 levels  
```{r}
dat[,.(acc_count=uniqueN(ApplicationID)),by=Loan_purpose][order(-acc_count)]

```

#### 8. PROMOTIONDESC
- **Type:** Factor
- **Description:** Description of the loan-taker.  
```{r}
unique(dat[,PROMOTIONDESC])
```

#### 9. CONSTITUTION
- **Type:** Factor
- **Description:** Type of the customer (Indiv, HUF, Proprietor, pvt ltd etc). Total 12 levels. 
```{r}
dat[,uniqueN(ApplicationID),by=CONSTITUTION]
```
#### 10. DISBDT
- **Type:** Date 
- **Description:** Date of disbursal of the loan. 
DISBDT is unique for each account. 

```{r}
dat[,DISBDT:=as.Date(DISBDT,format='%d-%m-%Y')]
```

##### Yearly distribution of disbursal
```{r}
dat[,.(account_count=uniqueN(ApplicationID)), by=year(DISBDT)][order(year)]
```

#### 11. due_date
- **Type:** Date
- **Description:** Date when the next EMI is due 
```{r}
dat[due_date=='',due_date:=NA]
dat[,due_date:=as.Date(due_date,format='%d-%m-%Y')]
```

#### 12. DISB_AMT
- **Type:** Numeric
- **Description:** Amount Disbursed. 
```{r}
dat[,DISB_AMT:=as.numeric(DISB_AMT)]
temp = dat[,.(amnt=mean(DISB_AMT)),by=ApplicationID]
hist(temp[,amnt],breaks=200,freq = FALSE)
```

#### 13. roi
- **Type:** Numeric
- **Description:** Rate of interest. For accounts with fixed rate, this will be constant. For Float roi accounts, roi is diff for every month. 
```{r}
dat[,roi:=as.numeric(roi)]
summary(dat[,roi])
```


#### 14. MANUFACTURERDESC
- **Type:** String
- **Description:** Name of Vehicle Manufacturer
```{r}
dat[,.(acc_count=uniqueN(ApplicationID)),by=MANUFACTURERDESC][order(-acc_count)]
```

#### 15. CATGDESC
- **Type:** Factor
- **Description:** Category of the Vehicle. 13 level
```{r}
dat[,.(acc_count=uniqueN(ApplicationID)),by=CATGDESC][order(-acc_count)]
```


#### 16. ASSETCOST
- **Type:** Numeric
- **Description:** Cost of the Vehicle. 

```{r}
dat[,ASSETCOST:=as.numeric(ASSETCOST)]
temp = dat[,.(amnt=mean(ASSETCOST)),by=ApplicationID]
hist(temp[,amnt],breaks=200,freq = FALSE)
```

#### 17. asset_level
- **Type:** Factor
- **Description:**  Classified in three levels based on the Price, make n model of the vehicle. Contains missing observations. 
```{r}
dat[,.(acc_count=uniqueN(ApplicationID)),asset_level][order(-acc_count)]
```
#### 18. woff_flag
- **Type:** Bool
- **Description:** Whether part of the loan was written off or not.  
```{r}
dat[,woff_flag:=woff_flag=='1']
dat[,.(acc_count=uniqueN(ApplicationID)),by=woff_flag]
```

#### 19. POS
- **Type:** Numeric 
- **Description:** Principal OutStanding. Part of the principal that is still unpaid. 
```{r}
dat[,POS:=as.numeric(POS)]
```
#### 20. DPD_Days
- **Type:** Integer
- **Description:** Days Past Delinquency
```{r}
dat[,DPD_Days:=as.integer(DPD_Days)]
dat[,.(acc_count=uniqueN(ApplicationID)),by=DPD_Days][order(DPD_Days)]
```
#### 21. NPA_since_date
- **Type:** Date
- **Description:** Date when the account first became NPA. Mu
```{r}
dat[NPA_since_date=='',NPA_since_date:=NA]
dat[,NPA_since_date:=as.Date(NPA_since_date,format='%d-%m-%Y')]
```
#### 22. Asof 
- **Type:** Date 
- **Description:** Snapshot date
```{r}
dat[,Asof:=as.Date(Asof,format='%d-%m-%Y')]
```

#### 23. Bounces
- **Type:** Bool
- **Description:** Flag whether any of the customers cheque/SI have bounced or not 
```{r}
dat[,Bounces:=Bounces!='']
```

#### 24. closed_status
- **Type:** 
- **Description:** 
```{r}
dat[,.(acc_count = uniqueN(ApplicationID)),by=closed_status]
dat[,closed_status:=closed_status=='C']
```

#### 25. Restructure_status
- **Type:** 
- **Description:** 
```{r}
dat[,Restructure_status:=Restructure_status=='Restructure']
```

#### 26. dq
- **Type:** Factor 
- **Description:** Levels of Delinquincy 
```{r}
unique(dat[,dq])
```
#### 27. ever_x, ever_30, ever_60
- **Type:** Bool
- **Description:** Whether the account has ever been to dq_x, dq_30 and dq_60 ever.  
```{r}
dat[,ever_x:=ever_x=='1']
dat[,ever_30:=ever_30=='1']
dat[,ever_60:=ever_60=='1']
```

#### 28. total_bounces
- **Type:** Integer
- **Description:** Total Number of times a cheque/SI has bounced
```{r}
dat[,total_bounces:=as.integer(total_bounces)]
summary(dat[,total_bounces])
```

#### 29. nonstarter, Quick_Mortality_Flag
- **Type:** Bool
- **Description:** 

```{r}
dat[,nonstarter:=nonstarter=="1"]
dat[,Quick_Mortality_Flag:=Quick_Mortality_Flag!=""]
dat[,.(acc_count=uniqueN(ApplicationID)),nonstarter]
dat[,.(acc_count=uniqueN(ApplicationID)),Quick_Mortality_Flag]
```

#### 30. Presentations
- **Type:** Bool
- **Description:** Whether a cheque was presented or not.

```{r}
dat[,Presentations:=Presentations=='1']
```

#### Valiable Selection

```{r}
a=c("ApplicationID",
    "AGREEMENT_NO",
"final_cif_no",
"Location",
"state",
"CV_Old_New_flag",
"Product",
"Loan_purpose",
"PROMOTIONDESC",
"CONSTITUTION",
"DISBDT",
"due_date",
"DISB_AMT",
"roi",
"MANUFACTURERDESC",
"CATGDESC",
"ASSETCOST",
"asset_level",
"woff_flag",
"POS",
"DPD_Days",
"Assets_Classification",
"NPA_since_date",
"Asof",
"Bounces",
"closed_status",
"Restructure_status",
"dq",
"ever_60",
"ever_30",
"ever_x",
"total_bounces",
"Quick_Mortality_Flag",
"Presentations")
dat2 = dat[,a,with=FALSE]
saveRDS(dat2,'data/cleaned_master_data.RDS')
```


